The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-13 article.tex
Added v for consistency

The CDK 1.0 and 1.2 implementations of the \texttt{IChemObjectBuilder} had,
however, one method for each data object constructor, resulting in a very large
interface. Moreover, this interface API had to be updated each time a new class
was introduced, and when existing methods changed and constructors were updated.
To simplify the API, the new \texttt{IChemObjectBuilder} collapses all methods
into a single method, which takes as a first parameter the class of the
interface that is to be constructed. All further parameters are passed as
parameters to the class constructor.

@@

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lcclc}
                             & Bit version  & Count version & CDK version & Default Size    \\
  CircularFingerprinter~\cite{rogers2010extended, Clark2014}      & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CircularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded.} \\
  EStateFingerprinter~\cite{Hall1995}       & $\checkmark$ &               & 1.2.0       & $79$            \\
  ExtendedFingerprinter      & $\checkmark$ &               & 1.0         & $1\,024$        \\
  Fingerprinter              & $\checkmark$ &               & 1.0         & $1\,024$        \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & 1.0         & $1\,024$        \\
  HybridizationFingerprinter & $\checkmark$ &               & 1.4.0       & $1\,024$        \\
  KlekotaRothFingerprinter~\cite{Klekota2008}   & $\checkmark$ &               & 1.4.6       & $4\,860$        \\
  LingoFingerprinter~\cite{vidal2005lingo}         & $\checkmark$ &               & \cdkversion{}     & NA%
\footnote[2]{The LingoFingerprinter does not have a default size.}
                                                                                             \\
  MACCSFingerprinter         & $\checkmark$ &               & 1.2.0       & $166$           \\
  PubchemFingerprinter~\cite{pubchemFP}       & $\checkmark$ &               & 1.4.0       & $881$            \\
  ShortestPathFingerprinter  & $\checkmark$ &               & \cdkversion{}     & $1\,024$        \\
  SignatureFingerprinter~\cite{signaturefingerprints}     & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $2^{32}$         \\
  SubstructureFingerprinter  & $\checkmark$ &               & 1.0         & $307$           \\

@@

\begin{tabular}{lll}
Toolkit                   & Time (s)   & Matched \\
\hline
CDK 1.4.9                 & 3,843  & 69,782  \\
CDK \cdkversion{}         & 67   & 62,518  \\
Open Babel 2.3.90         & 835 & 61,906  \\
RDKit 2016.3.4            & 378  & 62,402  \\
\end{tabular}

>>>>

The CDK v1.0 and v1.2 implementations of the \texttt{IChemObjectBuilder} had,
however, one method for each data object constructor, resulting in a very large
interface. Moreover, this interface API had to be updated each time a new class
was introduced, and when existing methods changed and constructors were updated.
To simplify the API, the new \texttt{IChemObjectBuilder} collapses all methods
into a single method, which takes as a first parameter the class of the
interface that is to be constructed. All further parameters are passed as
parameters to the class constructor.

@@

    \begin{minipage}{1\textwidth}
    \renewcommand*{\thempfootnote}{\fnsymbol{mpfootnote}}
    \centering
    \begin{tabular}{lcclc}
                             & Bit version  & Count version & CDK version & Default Size    \\
  CircularFingerprinter~\cite{rogers2010extended, Clark2014}      & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $1\,024$ / $2^{32}$%
\footnote[1]{For the CircularFingerprinter the bit version is folded to 1024 whereas the count version is unfolded.} \\
  EStateFingerprinter~\cite{Hall1995}       & $\checkmark$ &               & v1.2.0       & $79$            \\
  ExtendedFingerprinter      & $\checkmark$ &               & v1.0         & $1\,024$        \\
  Fingerprinter              & $\checkmark$ &               & v1.0         & $1\,024$        \\
  GraphOnlyFingerprinter     & $\checkmark$ &               & v1.0         & $1\,024$        \\
  HybridizationFingerprinter & $\checkmark$ &               & v1.4.0       & $1\,024$        \\
  KlekotaRothFingerprinter~\cite{Klekota2008}   & $\checkmark$ &               & v1.4.6       & $4\,860$        \\
  LingoFingerprinter~\cite{vidal2005lingo}         & $\checkmark$ &               & \cdkversion{}     & NA%
\footnote[2]{The LingoFingerprinter does not have a default size.}
                                                                                             \\
  MACCSFingerprinter         & $\checkmark$ &               & v1.2.0       & $166$           \\
  PubchemFingerprinter~\cite{pubchemFP}       & $\checkmark$ &               & v1.4.0       & $881$            \\
  ShortestPathFingerprinter  & $\checkmark$ &               & \cdkversion{}     & $1\,024$        \\
  SignatureFingerprinter~\cite{signaturefingerprints}     & $\checkmark$ & $\checkmark$  & \cdkversion{}     & $2^{32}$         \\
  SubstructureFingerprinter  & $\checkmark$ &               & v1.0         & $307$           \\

@@

\begin{tabular}{lll}
Toolkit                   & Time (s)   & Matched \\
\hline
CDK v1.4.9                 & 3,843  & 69,782  \\
CDK \cdkversion{}         & 67   & 62,518  \\
Open Babel 2.3.90         & 835 & 61,906  \\
RDKit 2016.3.4            & 378  & 62,402  \\
\end{tabular}
